Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-09 reports/revision_letter.Rmd
Add population and design to plots
Fixes #24
Fixes #22

>>>>

We agree that study design should have been a larger factor when choosing which effects to use.

We note that while limiting to certain study designs may improve the quality of the evidence, we are simply summarising what previous reviews have done.
that is, if previous reviews have not limited their evidence to certain designs (or moderated by design), we do not have that information to present.
We also found that there were not a lot of reviews which examined the same exposure and outcome, but differed on choice of study design.
When we included study design as part of our method of choosing effects, it only increased the number of effects by 5 (from 241 to 246).
That is, there are not a lot of instances where the same exposure and outcome are examined in different study designs.
